Regression Analysis—Simple

### 2019-03-28 figures/regression_analysis/regression_analysis_simple.rmd
updates to figures and labels—prepreparing for re-submission

```{r}
initial.cov.labels = c(
               "submission_year" = "Submission Year", 
               "submission_typeSR" = "Submission Type = SR", 
               "submission_typeTR" = "Submission Type = TR", 
               "ca_genderM" = "Corr. Author is Male",
               "ca_genderUNK" = "Corr. Author Gender UNK",
               "ca_institution_rankTop" = "Corr. Author Inst. Top",
               "ca_continentAfrica" = "Corr. author from Africa",
               "ca_continentAsia" = "Corr. author from Asia",
               "ca_continentEurope" = "Corr. author from Europe",
               "ca_continentOceania" = "Corr. author from Oceania",
               "ca_continentSouth America" = "Corr. author from South America"
               )

@@

### Plot the regression estimates for the initial submissions model
```{r}
initial_reg_plot <- plot_model(initial_model, 
           vline.color = "black", 
           #rm.terms = c("ca_genderUNK"),
           sort.est = TRUE, 
           show.values = TRUE, 
           value.offset = .3, 
           axis.labels = initial.cov.labels,
           wrap.labels = 100, # basically, don't wrap the labels, squeeze them all in
           title = "Encouragement of initial submissions",
           axis.lim = c(0.1, 10)) +
  theme_bw()

initial_reg_plot
```

@@

### Construct a table for the regression model for full submissions
```{r}
full.cov.labels = c("submission_year" = "Submission Year", 
               "submission_typeSR" = "Submission Type = SR", 
               "submission_typeTR" = "Submission Type = TR", 
               "fa_genderM" = "First Author is Male",
               "fa_genderUNK" = "First Author is Unknown Gender",
               "la_genderM" = "Last Author is Male",
               "la_institution_rankTop" = "Last Author Inst. Top",
               "la_continentAfrica" = "Last author from Africa",
               "la_continentAsia" = "Last author from Asia",
               "la_continentEurope" = "Last author from Europe",
               "la_continentOceania" = "Last author from Oceania",
               "la_continentSouth America" = "Last author from South America"
               )

@@

### Plot the regression estimates for full submissions
```{r}
full_reg_plot <- plot_model(full_model, 
           vline.color = "black", 
           sort.est = TRUE, 
           show.values = TRUE, 
           value.offset = .3, 
           axis.labels = full.cov.labels,
           wrap.labels = 100, # basically, don't wrap the labels, squeeze them all in
           title = "Acceptance of full submissions",
           axis.lim = c(0.1, 10)) +
  theme_bw()

full_reg_plot
```

### Arrange graphs
```{r}
regressions_simple <- grid.arrange(initial_reg_plot, full_reg_plot, ncol = 2)
```

### Save the output
```{r}
name <- paste0("~/Dropbox/eLife/elife-analysis/figures/main/", figure_name, figure_extension)
ggsave(name, plot = regressions_simple, height = 6, width = 10)
```

>>>>

```{r}
initial.cov.labels = c(
               "submission_year" = "Submission Year", 
               "submission_typeSR" = "Submission Type = SR", 
               "submission_typeTR" = "Submission Type = TR", 
               "ca_genderM" = "Corr. Author is Male",
               "ca_genderUNK" = "Corr. Author is Unknown Gender",
               "ca_institution_rankTop" = "Corr. Author Inst. Top",
               "ca_continentAfrica" = "Corr. Author from Africa",
               "ca_continentAsia" = "Corr. Author from Asia",
               "ca_continentEurope" = "Corr. Author from Europe",
               "ca_continentOceania" = "Corr. Author from Oceania",
               "ca_continentSouth America" = "Corr. Author from South America"
               )

@@

@@

### Construct a table for the regression model for full submissions
```{r}
full.cov.labels = c("submission_year" = "Submission Year", 
               "submission_typeSR" = "Submission Type = SR", 
               "submission_typeTR" = "Submission Type = TR", 
               "fa_genderM" = "First Author is Male",
               "fa_genderUNK" = "First Author is Unknown Gender",
               "la_genderM" = "Last Author is Male",
               "la_institution_rankTop" = "Last Author Inst. Top",
               "la_continentAfrica" = "Last Author from Africa",
               "la_continentAsia" = "Last Author from Asia",
               "la_continentEurope" = "Last Author from Europe",
               "la_continentOceania" = "Last Author from Oceania",
               "la_continentSouth America" = "Last Author from South America"
               )

@@

```{r}
initial_tidy <- tidy(initial_model, conf.int = T, exponentiate = T) %>%
  mutate(type = "Initial Submissions")
full_tidy <- tidy(full_model, conf.int = T, exponentiate = T) %>%
  mutate(type = "Full Submissions")

all_submissions <- rbind(initial_tidy, full_tidy)
```

```{r}
initial.plot <- initial_tidy %>%
  filter(term != "(Intercept)") %>%
  mutate(
    #type = factor(type, levels = c("Main Effects", "Global Interactions")),
    ast = sig2ast(p.value),
    ast.factor = factor(ast, 
                 levels = c("ns", ".", "*", "**", "***"), 
                 labels = c("p > 0.1", "p < 0.1", "p < 0.05", "p < 0.01", "p < 0.001")),
    color.sig = ifelse(p.value < 0.1, ifelse(estimate > 1, "Positive", "Negative"), "Not Signigicant"),
    term = as.factor(term),
    term = plyr::revalue(term, initial.cov.labels),
    term = reorder(term, estimate)
  ) %>%
  ggplot(aes(x = term, y = estimate, color = color.sig, shape = ast.factor)) +
  geom_point(size = 2.5) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  coord_flip() +
  #facet_grid(~type, scales = "free") +
  geom_text(aes(label = paste0(round(estimate, 3), 
                               ifelse(ast %in% c("ns", "."), "", ast)), 
                x = term, y = estimate), vjust = -0.6, hjust = -0.1, show.legend = F) +
  scale_color_manual(name = "Direction of Effect", values = c("firebrick", "grey", "blue")) +
  scale_shape_manual(name = "Significance Level", values = c(1, 10, 16, 17, 18), drop = F) +
  geom_hline(yintercept = 1, color = "black") +
  ylim(0.1, 6) +
  theme_minimal() +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_text(size = 9),
        plot.title = element_text(size = 12, face = "bold")) +
  labs(y = "Odds Ratio",
       title = "A. Initial Submissions")

initial.plot 
```

```{r}
full.plot <- full_tidy %>%
  filter(term != "(Intercept)") %>%
  mutate(
    ast = sig2ast(p.value),
    ast.factor = factor(ast, 
                 levels = c("ns", ".", "*", "**", "***"), 
                 labels = c("p > 0.1", "p < 0.1", "p < 0.05", "p < 0.01", "p < 0.001")),
    color.sig = ifelse(p.value < 0.1, ifelse(estimate > 1, "Positive", "Negative"), "Not Signigicant"),
    term = as.factor(term),
    term = plyr::revalue(term, full.cov.labels),
    term = reorder(term, estimate)
  ) %>%
  ggplot(aes(x = term, y = estimate, color = color.sig, shape = ast.factor)) +
  geom_point(size = 2.5) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  coord_flip() +
  #facet_grid(~type, scales = "free") +
  geom_text(aes(label = paste0(round(estimate, 3), 
                               ifelse(ast %in% c("ns", "."), "", ast)), 
                x = term, y = estimate), vjust = -0.6, hjust = -0.1, show.legend = F) +
  scale_color_manual(name = "Direction of Effect", values = c("firebrick", "grey", "blue")) +
  scale_shape_manual(name = "Significance Level", values = c(1, 10, 16, 15, 18), drop = F) +
  geom_hline(yintercept = 1, color = "black") +
  ylim(0.1, 6) +
  theme_minimal() +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_text(size = 9),
        plot.title = element_text(size = 12, face = "bold")) +
  labs(y = "Odds Ratio",
       title = "B. Full Submissions")

full.plot
```

```{r}
g_legend<-function(a.gplot){
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)}

mylegend <- g_legend(initial.plot)

both.plots <- grid.arrange(arrangeGrob(initial.plot + theme(legend.position="none"),
                         full.plot + theme(legend.position="none"),
                         nrow=1),
             mylegend, ncol=2,widths=c(10, 2))

both.plots
```

### Save the output
```{r}
name <- paste0("~/Dropbox/eLife/elife-analysis/figures/main/", figure_name, figure_extension)
ggsave(name, plot = both.plots, height = 6, width = 10)
```
